---
title: "econ_hw2"
author: "David Segan"
date: "4/22/2020"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}

# Load libraries and bring in data

library(tidyverse)
library(janitor)
library(stargazer)

mc_sector <- readxl::read_xlsx("HW2_Data.xlsx") %>% 
  clean_names()

```

### Question 1
##### Sector A

```{r}
# ----------------
# Sector A - MC curve
# ----------------

sector_a <- mc_sector %>% 
  select(abatement, mc_a)

sector_a_plot <- ggplot(sector_a, aes(x = abatement, y = mc_a)) + 
  geom_line() +
  labs(title = "Sector A estimates for marginal cost of abatement by abatement levels",
       x = "Abatement (Tons)",
       y = "Marginal Cost")

sector_a_plot

```

Marginal Cost = (m)*Abatement + (b)

```{r}
# -----------------
# Sector A - linear model overlayed with MC curve
# -----------------

lm_sector_a <- lm(mc_a ~ abatement, data = sector_a)
  
predict_df_a <- predict(lm_sector_a, sector_a)

df_a <- data.frame(sector_a, predict_df_a)

ggplot() +
  geom_line(data = lm_sector_a,
             aes(x = abatement,
                 y = mc_a),
             color = "coral",
             size = 1, 
             alpha = 1) +
  geom_line(data = df_a,
            aes(x = abatement,
                y = predict_df_a)) +
  theme_light() +
  labs(title = "Sector A predicted marginal cost of abatement by abatement levels",
       x = "Abatement (Tons)",
       y = "Marginal Cost")
```

```{r, results = "asis"}

# -----------
# Sector A - Linear model stats
# -----------

stargazer(lm_sector_a, type = "html")
```

##### Sector B
```{r sector B MC Curve}
# ----------------
# Sector B - MC curve
# ----------------
sector_b <- mc_sector %>% 
  select(abatement, mc_b)
sector_b_plot <- ggplot(sector_b, aes(x = abatement, y = mc_b)) + 
  geom_line() +
  labs(title = "Sector B estimates for marginal cost of abatement by abatement levels",
       x = "Abatement (Tons)",
       y = "Marginal Cost ($/ton)")
sector_b_plot
```

```{r B LM and MC}
# -----------
# Sector B - linear model overlayed with MC curve
# -----------
# Make a linear model for sector b:
linear_b <- lm(mc_b ~ abatement, data = mc_sector)
# Then, predict it back to the original data frame
predict_df_b <- mc_sector %>% 
  mutate(pred_b = predict(linear_b, mc_sector))
# And plot it
ggplot(data = predict_df_b) +
  geom_line(aes(x = abatement, y = mc_b),
            color = "lightsteelblue3",
            size = 1, 
            alpha = 1) +
  geom_line(aes(x = abatement, y = pred_b)) +
  
  theme_light() +
  labs(title = "Sector B predicted marginal cost of abatement by abatement levels",
       x = "Abatement (Tons)",
       y = "Marginal Cost")
  
```
Sector B Regression Table:
```{r B stargazer, results = "asis"}
stargazer(linear_b, type = "html")
```

##### Sector C
```{r}
# ----------------
# Sector C - MC curve
# ----------------

sector_c <- mc_sector %>%
  select(abatement, mc_c) %>%
  filter(abatement >= 40)

sector_c_plot <- ggplot(sector_c, aes(x = abatement, y = mc_c)) +
  geom_line() +
  labs(title = "Sector C estimates for marginal cost of abatement by abatement levels",
       x = "Abatement (Tons)",
       y = "Marginal Cost")

sector_c_plot

```

Marginal Cost = (m)*Abatement + (b)

```{r}
# -----------------
# Sector C - linear model overlayed with MC curve
# -----------------

lm_sector_c <- lm(mc_c ~ abatement, data = sector_c)
 
predict_df_c <- predict(lm_sector_c, sector_c)

df_c <- data.frame(sector_c, predict_df_c)

summary(lm_sector_c)

ggplot() +
  geom_line(data = lm_sector_c,
             aes(x = abatement,
                 y = mc_c),
             color = "coral",
             size = 1,
             alpha = 1) +
  geom_line(data = df_c,
            aes(x = abatement,
                y = predict_df_c)) +
  theme_light() +
  labs(title = "Sector C predicted marginal cost of abatement by abatement levels",
       x = "Abatement (Tons)",
       y = "Marginal Cost")
```

```{r, results = "asis"}

# -----------
# Sector C - Linear model stats
# -----------

stargazer(lm_sector_c, type = "html")

```


##### Sector D

```{r}
# ----------------
# Sector D - MC curve
# ----------------

sector_d <- mc_sector %>% 
  select(abatement, mc_d)

sector_d_plot <- ggplot(sector_d, aes(x = abatement, y = mc_d)) + 
  geom_line() +
  labs(title = "Sector D estimates for marginal cost of abatement by abatement levels",
       x = "Abatement (Tons)",
       y = "Marginal Cost")

sector_d_plot
```
```{r}
# -----------------
# Sector D - linear model overlayed with MC curve
# -----------------

lm_sector_d <- lm(mc_d ~ abatement, data = sector_d)

# poly_sector_d <- lm(mc_d ~ poly(abatement, 3, raw = TRUE, data = sector_d))

# exp_sector_d <- nls(mc_d ~ exp(a+b*abatement), raw = TRUE, data = sector_d)

predict_df_d <- predict(lm_sector_d, sector_d)

df_d <- data.frame(sector_d, predict_df_d)

ggplot() +
  geom_line(data = lm_sector_d,
             aes(x = abatement,
                 y = mc_d),
             color = "coral",
             size = 1, 
             alpha = 1) +
  geom_line(data = df_d,
            aes(x = abatement,
                y = predict_df_d)) +
  theme_light() +
  labs(title = "Sector D predicted marginal cost of abatement by abatement levels",
       x = "Abatement (Tons)",
       y = "Marginal Cost")
```

```{r, results = "asis"}

# -----------
# Sector D - Model stats
# -----------

stargazer(lm_sector_d, type = "html")
```


### Question 2
##### Demand for emissions

##### Sector A
```{r}

# Sector A
sector_a_new <- df_a %>% 
  mutate(q = 170-predict_df_a)

a_coeff = 0.513
a_const = 1.655
a_emissions_current = 170

a_supply <- function(abatement) {a_coeff*abatement + a_const}

a_price <- function(q) {
  a_coeff*(a_emissions_current-q) + a_const
}

q_pollution <- seq(0,300, by = 10)

a_demand_df <- data.frame(q_pollution)

a_demand_df <- a_demand_df %>% 
  mutate(a_price = a_price(q_pollution))

ggplot(data = a_demand_df, aes(x = q_pollution, y = a_price)) +
  geom_line()
```

##### Sector B

Now, we needa get demand curves from this. We know sector B currenty produces 200 tons of CO2.

We know the equation of the cost curves for abatement is...

price = 0.392 * abatement + 8.785

```{r B demand curve}
## b_coeff is the slope of the supply curve for abatement
## b_const is the intercept of the supply curve for abatement
b_coeff <- 0.392
b_const <- 8.785
b_emissions_current <- 200
  
# From these, we can make supply curves...
b_supply <- function(abatement) {b_coeff * abatement + b_const}
# b_supply_df <- b_demand_df %>% 
#   mutate(b_price = b_supply(q_pollution))
# 
# ggplot(b_supply_df, aes(x = q_pollution, y = b_price)) +
#   geom_line()
# And demand curves.
b_price <- function(q){
  b_coeff*(b_emissions_current - q) + b_const
}
# How do we apply this to our data, though?
# Let's make a list of some possible Q values, starting at 0, ending at 300.
q_pollution <- seq(0, 300, by = 10)
# And then, we can calculate a demand curve based on this...
# By first turning it into a data frame,
b_demand_df <- data.frame(q_pollution)
# Then applying the b_price function to the quantity of good produced:
b_demand_df <- b_demand_df %>% 
  mutate(b_price = b_price(q_pollution))
# Then we can plot it!
ggplot(data = b_demand_df, aes(x = q_pollution, y = b_price)) +
  geom_line()
```

##### Sector C
```{r}

# Sector C

sector_c_new <- df_c %>%
  mutate(q = 230-predict_df_c)

c_coeff = 1.390
c_const = -54.766
c_emissions_current = 230

c_supply <- function(abatement) {c_coeff*abatement + c_const}

c_demand <- function(q) {
  y = c_coeff*(c_emissions_current - q) + c_const
  return(y)
}

q_pollution_c <- seq(0, 300, by = 10)
c_demand_df <- data.frame(q_pollution_c)

c_demand_df <- c_demand_df %>%
  mutate(c_price = c_demand(q_pollution_c))

ggplot(c_demand_df, aes(x = q_pollution_c, y = c_price)) +
  geom_line()


```

##### Sector D
```{r}
# Sector D
d_coeff = 
d_const = 
d_emissions_current = 300

d_supply <- function(abatement) {y = d_coeff*abatement + d_const}

d_demand <- function(abatement) {y = d_coeff*(d_emissions_current-d_emissions_new)+d_const}

```

### Question 3
##### Policy options

#### Let's first calculate aggregate supply and demand curves

Supply:

We have all of our supply equations. We know that the aggregate abatement supply is the horizontal sum of all these curves...
but, we're currently predicting the price from Q. So, we need to rearrange all these equations so they spit out a q:

```{r}
# Let's predict a df for all of these...

abatement_agg <- seq(0, 500, by = 10)
agg_abate_df <- data.frame(abatement_agg)
agg_abate_df <- agg_abate_df %>% 
  mutate(a_price = a_supply(abatement_agg)) %>% 
  mutate(b_price = b_supply(abatement_agg)) %>% 
  mutate(c_price = c_supply(abatement_agg))
```

Then, we can make a new set of lm's for `quantity` as a function of `price`:

```{r}
q_lm_a <- lm(abatement_agg ~ a_price, data = agg_abate_df)
q_lm_b <- lm(abatement_agg ~ b_price, data = agg_abate_df)
q_lm_c <- lm(abatement_agg ~ c_price, data = agg_abate_df)
```

And then we can project this onto a new data frame, with prices.

First we gotta make new functions for all of em...

```{r}
q_lm_a
a_abatement_fx <- function(price) {
  1.949 * price - 3.226
}
q_lm_b
b_abatement_fx <- function(price) {
  2.551 * price - 22.411
}
q_lm_c 
c_abatement_fx <- function(price) {
  0.7194 * price + 39.400
}
# Then, we can predict a new df for price...and them sum them for total abatement at a given price.
price <- seq(0, 300, by = 10)
q_pred_df <- data.frame(price)

q_pred_df <- q_pred_df %>% 
  mutate(q_a = a_abatement_fx(price)) %>% 
  mutate(q_b = b_abatement_fx(price)) %>% 
  mutate(q_c = c_abatement_fx(price)) %>% 
  mutate(total_abate = q_a + q_b + q_c)
```

And then, we can pull a lm for the sum total.

```{r}
total_abatement <- lm(total_abate ~ price, data = q_pred_df)
total_abatement

# And then write a function...
tot_abate_fx <- function(price){
  5.219 * price + 13.763
}

```




##### a. Cap on carbon
```{r}
# Sectors A, B, and C capped at 300 tons


```

##### For sector B:
Must cut emissions by 100 tons.
We know B is producing 200 tons right now, so that ends with 100 tons.
We can find the price by plugging 100 tons into the supply curve (supply curve is for abatement...)

```{r}
cost b_price(100)
```


##### b. Tax on carbon
```{r}
# What tax accomplishes desired reduction of 300 tons


```

##### c. Cap and trade
```{r}
# Outcome of trading if each sector gets 100 carbon credits


```

### Question 4
##### Should country X (sector D) join a carbon cap and trade market in country Y?



