---
title: "econ_hw2"
author: "David Segan, Gavi Keyles, Gabe De La Rosa"
date: "4/22/2020"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}

# Load libraries and bring in data

library(tidyverse)
library(janitor)
library(stargazer)

mc_sector <- readxl::read_xlsx("HW2_Data.xlsx") %>% 
  clean_names()

```

### Question 1
##### Sector A

```{r}
# ----------------
# Sector A - MC curve
# ----------------

sector_a <- mc_sector %>% 
  select(abatement, mc_a)

sector_a_plot <- ggplot(sector_a, aes(x = abatement, y = mc_a)) + 
  geom_line() +
  labs(title = "Sector A estimates for marginal cost of abatement by abatement levels",
       x = "Abatement (Tons)",
       y = "Marginal Cost")

sector_a_plot

```

Marginal Cost = (m)*Abatement + (b)

```{r}
# -----------------
# Sector A - linear model overlayed with MC curve
# -----------------

lm_sector_a <- lm(mc_a ~ abatement, data = sector_a)
  
predict_df_a <- predict(lm_sector_a, sector_a)

df_a <- data.frame(sector_a, predict_df_a)

ggplot() +
  geom_line(data = lm_sector_a,
             aes(x = abatement,
                 y = mc_a),
             color = "coral",
             size = 1, 
             alpha = 1) +
  geom_line(data = df_a,
            aes(x = abatement,
                y = predict_df_a)) +
  theme_light() +
  labs(title = "Sector A predicted marginal cost of abatement by abatement levels",
       x = "Abatement (Tons)",
       y = "Marginal Cost")
```

```{r, results = "asis"}

# -----------
# Sector A - Linear model stats
# -----------

stargazer(lm_sector_a, type = "html")
```

##### Sector B
```{r sector B MC Curve}
# ----------------
# Sector B - MC curve
# ----------------
sector_b <- mc_sector %>% 
  select(abatement, mc_b)
sector_b_plot <- ggplot(sector_b, aes(x = abatement, y = mc_b)) + 
  geom_line() +
  labs(title = "Sector B estimates for marginal cost of abatement by abatement levels",
       x = "Abatement (Tons)",
       y = "Marginal Cost ($/ton)")
sector_b_plot
```

```{r B LM and MC}
# -----------
# Sector B - linear model overlayed with MC curve
# -----------
# Make a linear model for sector b:
linear_b <- lm(mc_b ~ abatement, data = mc_sector)
# Then, predict it back to the original data frame
predict_df_b <- mc_sector %>% 
  mutate(pred_b = predict(linear_b, mc_sector))
# And plot it
ggplot(data = predict_df_b) +
  geom_line(aes(x = abatement, y = mc_b),
            color = "lightsteelblue3",
            size = 1, 
            alpha = 1) +
  geom_line(aes(x = abatement, y = pred_b)) +
  
  theme_light() +
  labs(title = "Sector B predicted marginal cost of abatement by abatement levels",
       x = "Abatement (Tons)",
       y = "Marginal Cost")
  
```
Sector B Regression Table:
```{r B stargazer, results = "asis"}
stargazer(linear_b, type = "html")
```

##### Sector C
```{r}
# ----------------
# Sector C - MC curve
# ----------------

sector_c <- mc_sector %>%
  select(abatement, mc_c) %>%
  filter(abatement >= 40)

sector_c_plot <- ggplot(sector_c, aes(x = abatement, y = mc_c)) +
  geom_line() +
  labs(title = "Sector C estimates for marginal cost of abatement by abatement levels",
       x = "Abatement (Tons)",
       y = "Marginal Cost")

sector_c_plot

```

Marginal Cost = (m)*Abatement + (b)

```{r}
# -----------------
# Sector C - linear model overlayed with MC curve
# -----------------

lm_sector_c <- lm(mc_c ~ abatement, data = sector_c)
 
predict_df_c <- predict(lm_sector_c, sector_c)

df_c <- data.frame(sector_c, predict_df_c)

# summary(lm_sector_c)

ggplot() +
  geom_line(data = lm_sector_c,
             aes(x = abatement,
                 y = mc_c),
             color = "coral",
             size = 1,
             alpha = 1) +
  geom_line(data = df_c,
            aes(x = abatement,
                y = predict_df_c)) +
  theme_light() +
  labs(title = "Sector C predicted marginal cost of abatement by abatement levels",
       x = "Abatement (Tons)",
       y = "Marginal Cost")
```

```{r, results = "asis"}

# -----------
# Sector C - Linear model stats
# -----------

stargazer(lm_sector_c, type = "html")

```


##### Sector D

```{r}
# ----------------
# Sector D - MC curve
# ----------------

sector_d <- mc_sector %>% 
  select(abatement, mc_d)

sector_d_plot <- ggplot(sector_d, aes(x = abatement, y = mc_d)) + 
  geom_line() +
  labs(title = "Sector D estimates for marginal cost of abatement by abatement levels",
       x = "Abatement (Tons)",
       y = "Marginal Cost")

sector_d_plot
```
```{r}
# -----------------
# Sector D - linear model overlayed with MC curve
# -----------------

lm_sector_d <- lm(mc_d ~ abatement, data = sector_d)

# poly_sector_d <- lm(mc_d ~ poly(abatement, 3, raw = TRUE, data = sector_d))

# exp_sector_d <- nls(mc_d ~ exp(a+b*abatement), raw = TRUE, data = sector_d)

predict_df_d <- predict(lm_sector_d, sector_d)

df_d <- data.frame(sector_d, predict_df_d)

ggplot() +
  geom_line(data = lm_sector_d,
             aes(x = abatement,
                 y = mc_d),
             color = "coral",
             size = 1, 
             alpha = 1) +
  geom_line(data = df_d,
            aes(x = abatement,
                y = predict_df_d)) +
  theme_light() +
  labs(title = "Sector D predicted marginal cost of abatement by abatement levels",
       x = "Abatement (Tons)",
       y = "Marginal Cost")
```

```{r, results = "asis"}

# -----------
# Sector D - Model stats
# -----------

stargazer(lm_sector_d, type = "html")
```

##### All sectors marginal abatement costs

```{r}

predict_mac_all <- data.frame(predict_df_a, predict_df_b, predict_df_c, predict_df_d)

# ggplot() +
#   geom_line(data = df_a,
#             aes(x = abatement,
#                 y = predict_df_a)) +
#   geom_line(data = predict_df_b,
#             aes(x = abatement,
#                 y = predict_df_b)) +
#   geom_line(data = df_c,
#             aes(x = abatement,
#                 y = predict_df_c)) +
#   geom_line(data = df_d,
#             aes(x = abatement,
#                 y = predict_df_d)) +
#   theme_light() +
#   labs(title = "All sectors predicted marginal cost of abatement by abatement levels",
#        x = "Abatement (Tons)",
#        y = "Marginal Cost")
```



### Question 2
##### Demand for emissions

##### Sector A
```{r}

# Sector A
sector_a_new <- df_a %>% 
  mutate(q = 170-predict_df_a)

a_coeff = 0.513
a_const = 1.655
a_emissions_current = 170

a_supply <- function(abatement) {a_coeff*abatement + a_const}

a_price <- function(q) {
  a_coeff*(a_emissions_current-q) + a_const
}

q_pollution <- seq(0,300, by = 10)

a_demand_df <- data.frame(q_pollution)

a_demand_df <- a_demand_df %>% 
  mutate(a_price = a_price(q_pollution))

ggplot(data = a_demand_df, aes(x = q_pollution, y = a_price)) +
  geom_line()
```

##### Sector B

Now, we needa get demand curves from this. We know sector B currenty produces 200 tons of CO2.

We know the equation of the cost curves for abatement is...

price = 0.392 * abatement + 8.785

```{r B demand curve}
## b_coeff is the slope of the supply curve for abatement
## b_const is the intercept of the supply curve for abatement
b_coeff <- 0.392
b_const <- 8.785
b_emissions_current <- 200
  
# From these, we can make supply curves...
b_supply <- function(abatement) {b_coeff * abatement + b_const}
# b_supply_df <- b_demand_df %>% 
#   mutate(b_price = b_supply(q_pollution))
# 
# ggplot(b_supply_df, aes(x = q_pollution, y = b_price)) +
#   geom_line()
# And demand curves.
b_price <- function(q){
  b_coeff*(b_emissions_current - q) + b_const
}
# How do we apply this to our data, though?
# Let's make a list of some possible Q values, starting at 0, ending at 300.
q_pollution <- seq(0, 300, by = 10)
# And then, we can calculate a demand curve based on this...
# By first turning it into a data frame,
b_demand_df <- data.frame(q_pollution)
# Then applying the b_price function to the quantity of good produced:
b_demand_df <- b_demand_df %>% 
  mutate(b_price = b_price(q_pollution))
# Then we can plot it!
ggplot(data = b_demand_df, aes(x = q_pollution, y = b_price)) +
  geom_line()
```

##### Sector C
```{r}

# Sector C

sector_c_new <- df_c %>%
  mutate(q = 230-predict_df_c)

c_coeff = 1.390
c_const = -54.766
c_emissions_current = 230

c_demand <- function(q) {
  y = c_coeff*(c_emissions_current - q) + c_const
  return(y)
}

q_pollution_c <- seq(0, 300, by = 10)
c_demand_df <- data.frame(q_pollution_c)

c_demand_df <- c_demand_df %>%
  mutate(c_price = c_demand(q_pollution_c))

ggplot(c_demand_df, aes(x = q_pollution_c, y = c_price)) +
  geom_line()


```

##### Sector D
```{r}
# Sector D
d_coeff = 0.553
d_const = -12.197
d_emissions_current = 300

d_supply <- function(abatement) {d_coeff*abatement + d_const}

d_price <- function(q) {
  a_coeff*(d_emissions_current-q) + d_const
}

q_pollution <- seq(0,300, by = 10)

d_demand_df <- data.frame(q_pollution)

d_demand_df <- d_demand_df %>% 
  mutate(d_price = d_price(q_pollution))

ggplot(data = d_demand_df, aes(x = q_pollution, y = d_price)) +
  geom_line()

```

### Question 3
##### Policy options

For each policy:
(1) the total cost of meeting the target in country X,
(2) the cost (or benefit) to each sector
(3) the tax revenue generated.

##### a. Cap on carbon
```{r}
# Sectors A, B, and C each cut emissions by 100. new total is 300 tons.


```

##### b. Tax on carbon
```{r}
# What tax accomplishes desired reduction of 300 tons


```

##### c. Cap and trade
```{r}
# Outcome of trading if each sector gets 100 carbon credits


```

### Question 4
##### Should country X (sector D) join a carbon cap and trade market in country Y?



