---
title: "econ_hw2_clean"
author: "David Segan, Gavi Keyles, Gabe De La Rosa"
date: "4/26/2020"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r, include = FALSE}
# Load libraries and bring in data
library(tidyverse)
library(janitor)
library(stargazer)
mc_sector <- readxl::read_xlsx("HW2_Data.xlsx") %>% 
  clean_names()
```

```{r}
# Linear models of marginal abatement costs by sector
lm_sector_a <- lm(mc_a ~ abatement, data = mc_sector)
lm_sector_b <- lm(mc_b ~ abatement, data = mc_sector)
lm_sector_c <- lm(mc_c ~ abatement, data = mc_sector)
lm_sector_d <- lm(mc_d ~ abatement, data = mc_sector)

# Naming coefficients and current emission levels
# coeff = abatement coefficient (slope of MAC curve)
# const = constant (intercept of MAC curve)

a_coeff <- lm_sector_a$coefficients[2]
a_const <- lm_sector_a$coefficients[1]
b_coeff <- lm_sector_b$coefficients[2]
b_const <- lm_sector_b$coefficients[1]
c_coeff <- lm_sector_c$coefficients[2]
c_const <- lm_sector_c$coefficients[1]
d_coeff <- lm_sector_d$coefficients[2]
d_const <- lm_sector_d$coefficients[1]

# Current emissions
a_emissions_current <- 170
b_emissions_current <- 200
c_emissions_current <- 230
d_emissions_current <- 300

# Supply curves for price (marginal abatement costs)
a_supply <- function(abatement) {a_coeff*abatement + a_const}
b_supply <- function(abatement) {b_coeff*abatement + b_const}
c_supply <- function(abatement) {c_coeff*abatement + c_const}
d_supply <- function(abatement) {d_coeff*abatement + d_const}

# Supply curves for Abatement

a_abatement <- function(a_supply){(a_supply - a_const)/a_coeff}
b_abatement <- function(b_supply){(b_supply - b_const)/b_coeff}
c_abatement <- function(c_supply){(c_supply - c_const)/c_coeff}
d_abatement <- function(d_supply){(d_supply - d_const)/d_coeff}

# Demand curves for price (marginal benefit of each additional ton of pollution)

a_price <- function(pollution) {a_coeff*(a_emissions_current - pollution) + a_const}
b_price <- function(pollution) {b_coeff*(b_emissions_current - pollution) + b_const}
c_price <- function(pollution) {c_coeff*(c_emissions_current - pollution) + c_const}
d_price <- function(pollution) {d_coeff*(d_emissions_current - pollution) + d_const}

# Demand curves for emissions

a_pollution <- function(a_price) {a_emissions_current - ((a_price - a_const)/a_coeff)}
b_pollution <- function(b_price) {b_emissions_current - ((b_price - b_const)/b_coeff)}
c_pollution <- function(c_price) {c_emissions_current - ((c_price - c_const)/c_coeff)}
d_pollution <- function(d_price) {d_emissions_current - ((d_price - d_const)/d_coeff)}
```

View Linear Models

```{r}
lm_sector_a
lm_sector_b
lm_sector_c
lm_sector_d
```


### Question 1

Marginal Cost of Abatement = (m)*Abatement + (b)

##### Sector A
```{r}
# -----------------
# Sector A - linear model overlayed with MC curve
# -----------------

sector_a <- mc_sector %>% 
  select(abatement, mc_a)
predict_df_a <- predict(lm_sector_a, sector_a)
df_a <- data.frame(sector_a, predict_df_a)
ggplot() +
  geom_line(data = lm_sector_a,
             aes(x = abatement,
                 y = mc_a),
             color = "darkgreen",
             size = 1, 
             alpha = 1) +
  geom_line(data = df_a,
            aes(x = abatement,
                y = predict_df_a)) +
  theme_light() +
  labs(title = "Sector A predicted marginal cost of abatement by abatement levels",
       x = "Abatement (Tons)",
       y = "Marginal Cost")
```

```{r, results = "asis"}
# -----------
# Sector A - Linear model stats
# -----------
stargazer(lm_sector_a, type = "html")
```

##### Sector B
```{r B LM and MC}
# -----------
# Sector B - linear model overlayed with MC curve
# -----------
sector_b <- mc_sector %>% # Select data
  select(abatement, mc_b) 
predict_df_b <- mc_sector %>% # predict it back to the original data frame
  mutate(pred_b = predict(lm_sector_b, mc_sector))
df_b <- data.frame(sector_b, predict_df_b) # data frame with both actual mc and predicted
ggplot(data = predict_df_b) + # And plot it
  geom_line(aes(x = abatement, y = mc_b),
            color = "lightsteelblue3",
            size = 1, 
            alpha = 1) +
  geom_line(aes(x = abatement, y = pred_b)) +
  theme_light() +
  labs(title = "Sector B predicted marginal cost of abatement by abatement levels",
       x = "Abatement (Tons)",
       y = "Marginal Cost")
  
```

```{r B stargazer, results = "asis"}
# -----------
# Sector B - Linear model stats
# -----------
stargazer(lm_sector_b, type = "html")
```

##### Sector C
```{r}
# -----------------
# Sector C - linear model overlayed with MC curve
# -----------------
sector_c <- mc_sector %>%
  select(abatement, mc_c) 
predict_df_c <- predict(lm_sector_c, sector_c)
df_c <- data.frame(sector_c, predict_df_c)
ggplot() +
  geom_line(data = lm_sector_c,
             aes(x = abatement,
                 y = mc_c),
             color = "red",
             size = 1,
             alpha = 1) +
  geom_line(data = df_c,
            aes(x = abatement,
                y = predict_df_c)) +
  theme_light() +
  labs(title = "Sector C predicted marginal cost of abatement by abatement levels",
       x = "Abatement (Tons)",
       y = "Marginal Cost")
```

```{r, results = "asis"}
# -----------
# Sector C - Linear model stats
# -----------
stargazer(lm_sector_c, type = "html")
```
##### Sector D
```{r}
# -----------------
# Sector D - linear model overlayed with MC curve
# -----------------
sector_d <- mc_sector %>% 
  select(abatement, mc_d)
predict_df_d <- predict(lm_sector_d, sector_d)
df_d <- data.frame(sector_d, predict_df_d)
ggplot() +
  geom_line(data = lm_sector_d,
             aes(x = abatement,
                 y = mc_d),
             color = "coral",
             size = 1, 
             alpha = 1) +
  geom_line(data = df_d,
            aes(x = abatement,
                y = predict_df_d)) +
  theme_light() +
  labs(title = "Sector D predicted marginal cost of abatement by abatement levels",
       x = "Abatement (Tons)",
       y = "Marginal Cost")
```

```{r, results = "asis"}
# -----------
# Sector D - Model stats
# -----------
stargazer(lm_sector_d, type = "html")
```

```{r all sectors marginal abatement costs}
# -----------
# All sectors - Marginal abatement costs
# -----------
ggplot() +
  geom_line(data = df_a,
            aes(x = abatement,
                y = predict_df_a),
            color = "darkgreen",
            size = 1,
            alpha = 1) +
  geom_line(data = df_b,
            aes(x = abatement, y = pred_b),
            color = "lightsteelblue3",
            size = 1,
            alpha = 1) +
  geom_line(data = df_c,
            aes(x = abatement,
                y = predict_df_c),
            color = "red",
            size = 1, 
            alpha = 1) +
  geom_line(data = df_d,
            aes(x = abatement,
                y = predict_df_d),
            color = "coral",
             size = 1, 
             alpha = 1) +
  theme_light() +
  labs(title = "All sectors predicted marginal cost of abatement by abatement levels",
       x = "Abatement (Tons)",
       y = "Marginal Cost ($/ton)")
```

### Question 2
##### Demand for emissions
```{r full demand curve}
# -----------
# All sectors - demand curve
# -----------
q_pollution <- seq(0,300, by = 10) # Make a list of pollution values
full_demand_df <- data.frame(q_pollution) # Add it into a df
full_demand_df <- full_demand_df %>% # Calculate each sector's price..
  mutate(a_price = a_price(q_pollution)) %>% 
  mutate(b_price = b_price(q_pollution)) %>% 
  mutate(c_price = c_price(q_pollution)) %>% 
  mutate(d_price = d_price(q_pollution))

# Repeat for prices:

p_pollution <- seq(0,300, by = 10) # Make a list of prices
full_demand_p_df <- data.frame(p_pollution) # Add it into a df

full_demand_p_df <- full_demand_p_df %>% # Calculate each sector's price..
  mutate(a_pollution = a_pollution(p_pollution)) %>% 
  mutate(b_pollution = b_pollution(p_pollution)) %>%
  mutate(c_pollution = c_pollution(p_pollution)) %>% 
  mutate(d_pollution = d_pollution(p_pollution)) %>% 
  mutate(total_pollution = a_pollution + b_pollution + c_pollution + d_pollution)

ggplot(data = full_demand_p_df, aes(y = p_pollution)) + # graph it
  geom_line(aes(x = a_pollution),
            color = "darkgreen") +
  geom_line(aes(x = b_pollution),
            color = "lightsteelblue3") +
  geom_line(aes(x = c_pollution),
            color = "red") +
  geom_line(aes(x = d_pollution),
            color = "coral") # +
  # geom_line(aes(x = total_pollution),
  #          color = "black") +
  scale_x_continuous(limits = c(0, 1000),
                     expand = c(0,0))

```

### Question 3
##### Policy options
For each policy:
(1) the total cost of meeting the target in country X,
(2) the cost (or benefit) to each sector
(3) the tax revenue generated.

```{r abatement functions and graph}
## --------
## Full abatement curve
## --------
price_abatement <- seq(0,300, by = 10) # Make a list of prices
full_abatement_p_df <- data.frame(price_abatement) # Add it into a df

full_abatement_p_df <- full_demand_p_df %>% # Calculate each sector's price..
  mutate(a_abatement = a_abatement(price_abatement)) %>% 
  mutate(b_abatement = b_abatement(price_abatement)) %>%
  mutate(c_abatement = c_abatement(price_abatement)) %>% 
  mutate(d_abatement = d_abatement(price_abatement)) %>% 
  mutate(total_abatement_X = a_abatement + b_abatement + c_abatement)

ggplot(data = full_abatement_p_df, aes(y = price_abatement)) + # graph it
  geom_line(aes(x = a_abatement),
            color = "darkgreen") +
  geom_line(aes(x = b_abatement),
            color = "lightsteelblue3") +
  geom_line(aes(x = c_abatement),
            color = "red") +
  geom_line(aes(x = d_abatement),
            color = "coral") +
  geom_line(aes(x = total_abatement_X),
           color = "black") +
  scale_x_continuous(limits = c(0, 1000),
                     expand = c(0,0))
```

```{r total abatement quantity and price functions}
## --------
## Aggregate abatement model given abatement
## --------
lm_total_abatement <- lm(total_abatement_X ~ price_abatement, data = full_abatement_p_df) # LM of the total line
total_abatement_coeff <- lm_total_abatement$coefficients[2]
total_abatement_const <- lm_total_abatement$coefficients[1]
total_abatement_fx <- function(price_abatement){total_abatement_coeff * price_abatement + total_abatement_const} # Function from the LM

lm_total_price_a <- lm(price_abatement ~ total_abatement_X, data = full_abatement_p_df)
total_abatement_p_coeff <- lm_total_price_a$coefficients[2]
total_abatement_p_const <- lm_total_price_a$coefficients[1]
total_abatement_p_fx <- function(total_abatement){
  total_abatement_p_coeff * total_abatement +total_abatement_p_const
} 
```

##### a. Cap on carbon
##### (1) total cost of meeting the target in country X
```{r 300 ton cap on carbon}
##---------
## Total cost to country X:
##---------
a_cap_cost <- integrate(a_supply, lower = 0, upper = 100) # First, we calculate cost to each sector
b_cap_cost <- integrate(b_supply, lower = 0, upper = 100)
c_cap_cost <- integrate(c_supply, lower = 0, upper = 100)
X_cap_cost <- a_cap_cost$value[1] + b_cap_cost$value[1] + c_cap_cost$value[1] # Then add them
X_cap_cost
```
##### (2) cost to each sector:
```{r}
# See above
a_cap_cost$value[1]
b_cap_cost$value[1]
c_cap_cost$value[1]
```
##### (3) tax revenue generated:
```{r}
# Zero!
```
##### b. Tax on carbon
```{r}
##-------
## Abatement tax:
##-------
abatement_tax <- total_abatement_p_fx(300) # What tax accomplishes desired reduction of 300 tons?
abatement_tax
```

##### (1) total cost of meeting this target to country x:
```{r}
## -------
## Cost to country X with a tax:
## -------
X_cost_tax <- integrate(total_abatement_p_fx, lower = 0, upper = 300) # Integral of the aggregate abatement curve...
X_cost_tax$value[1]
X_revenue_tax <- (300 * abatement_tax)
X_total_cost <- (X_cost_tax$value[1] - X_revenue_tax)
X_total_cost # So, they actually benefit.
```
##### (2) cost to each sector:
```{r}
## -------
## Cost to each sector with a tax:
## -------
a_tax_abated <- a_abatement(abatement_tax) # Quantity each sector abates...
b_tax_abated <- b_abatement(abatement_tax)
c_tax_abated <- c_abatement(abatement_tax)
a_tax_cost <- integrate(a_supply, lower = 0, upper = a_tax_abated) # Cost under the abatement curves
b_tax_cost <- integrate(b_supply, lower = 0, upper = b_tax_abated)
c_tax_cost <- integrate(c_supply, lower = 0, upper = c_tax_abated)
a_tax_cost$value[1]
b_tax_cost$value[1]
c_tax_cost$value[1]
```

##### (3) tax revenue generated:

```{r}
## -------
## Revenue from the tax:
## -------
X_revenue_tax <- (300 * abatement_tax)
X_revenue_tax
```
##### c. Cap and trade
##### (1) Cost to Country X:
```{r}
# Outcome of trading if each sector gets 100 carbon credits
permit_trading_price <- total_abatement_p_fx(300) # First, get equilibrium trading price
permits_traded_a <- a_abatement(permit_trading_price)# Now, plug into individual abatement functions
permits_traded_b <- b_abatement(permit_trading_price)# This is the total q each sector abates
permits_traded_c <- c_abatement(permit_trading_price)
permits_traded_a + permits_traded_b + permits_traded_c # Let's check that they add up to 300

### This isn't used ###
diff_a_3c <- integrate(a_abatement, permits_traded_a, 100)$value # Integrate to find costs per sector
diff_b_3c <- integrate(b_abatement, permits_traded_b, 100)$value # The difference in cost between a CAP and a CAP AND TRADE to each sector.
diff_c_3c <- integrate(c_abatement, permits_traded_c, 100)$value
### --- ###

cost_CT_a <- integrate(a_abatement, 0, permits_traded_a)$value # Integrate from 0 to new trading equilibrium to find the abatement costs to each sector.
cost_CT_b <- integrate(b_abatement, 0, permits_traded_b)$value
cost_CT_c <- integrate(c_abatement, 0, permits_traded_c)$value
cost_CT_a
cost_CT_b
cost_CT_c

# Total country cost
country_cost_3c <- integrate(total_abatement_fx, 0, 300)$value
```


```{r}
# David can delete all of this

# Sector efficient quantity to abate
# When total quantity abated is 300, gives us a marginal cost - we want it to be the same for all sectors to be efficient. Then, abatement_fx gives us a q

a_abate_ct <- a_abatement_fx(tot_abate_p_fx(300))

b_abate_ct <- b_abatement_fx(tot_abate_p_fx(300))

c_abate_ct <- c_abatement_fx(tot_abate_p_fx(300))

# How do those values compare to if just reduced by 100?

a_abate_no_trade <- 100
b_abate_no_trade <- 100
c_abate_no_trade <- 100

# Units to be traded (negative means trading)

a_trade <- a_abate_ct - a_abate_no_trade
b_trade <- b_abate_ct - b_abate_no_trade
c_trade <- c_abate_ct - c_abate_no_trade

# Cost to each sector of just their abatement 
a_ct_cost <- integrate(a_supply, lower = 0, upper = a_abate_ct)
b_ct_cost <- integrate(b_supply, lower = 0, upper = b_abate_ct)
c_ct_cost <- integrate(c_supply, lower = 0, upper = c_abate_ct)

# Benefits / Costs of trade
a_ct_net <- 2927.586 - (a_trade*tot_abate_p_fx(300))
b_ct_net <- 3736.323 - (b_trade*tot_abate_p_fx(300))
c_ct_net <- 1400.3 - (c_trade*tot_abate_p_fx(300))

a_ct_net
b_ct_net
c_ct_net
```

### Question 4
##### Should country X (sector D) join a carbon cap and trade market in country Y?

```{r}
# Country Y:
# current emissions: 300 tons per year

# Basically, we need to add sector D to the abatement graph then calculate a new aggregate cost curve

lm_sector_d

# Predicts the price...
sector_d_cost_fx <- function(abatement){
  0.5533 * abatement - 12.1969
}

# Predicts the quantity...
sector_d_q_fx <- function(price){
  (price + 12.1969) / 0.5533
}

# Add them together in a df, then make an aggregate quantity column...
agg_abate_d_df <-  q_pred_df %>% 
  mutate(q_d = sector_d_q_fx(price)) %>% 
  mutate(q_agg = q_a + q_b + q_c + q_d)


ggplot(agg_abate_d_df, aes(y = price)) +
  geom_line(aes(x = q_a),
            color = "red") +
  geom_line(aes(x = q_b),
            color = "blue") +
  geom_line(aes(x = q_c),
            color = "green") +
  geom_line(aes(x = q_d),
            color = "yellow") +
  geom_line(aes(x = q_agg))
  
# Make a new aggregate cost curve and function

agg_abate_d <- lm(price ~ q_agg, data = agg_abate_d_df)

agg_abate_d

agg_abate_d_fx <- function(abatement){
  0.1423 * abatement - 5.0958
}

# And then use it to get the price. Note that the new total emissions is 600 tons

agg_abate_d_fx(600)

# Price of carbon is $80.2842 per ton

# How much will each sector produce?

# I want a quantity, given a price:

a_abatement_fx(80.2842)
# 153.2497

b_abatement_fx(80.2842)
# 182.394

c_abatement_fx(80.2842)
# 97.15645

sector_d_q_fx(80.2842)

# 167.1446


#####
# to double check...
# 153.2497 + 182.394 + 97.15645 + 167.1446 = 600!

# I can quantify the  benefit to Country Y (sector D):

# We know the price per ton of carbon is $80.2842
# And they're allotted 300 tons
# And we predict they'd produce 167.1446

##-------------
# I'm stuck here. What price does D sell its credits at??
##-------------

# I think its the area under the curve for D, or the area from abating zero units to the market efficient number of units (167 or whatever...)

# So the cost to them is...

80.2842 * (300-167.1446)

# They would make $10,666.19 selling carbon credits.


```

